\begingroup
\RaggedRight

I would like to express my sincere appreciation and gratitude to Dr. Amin Rezaei, my esteemed thesis advisor, for his invaluable guidance and unwavering support throughout the research journey. Dr. Rezaei played a pivotal role in shaping my research experience, and his patience and dedication have been instrumental in bringing this thesis to fruition.

I also express my heartfelt gratitude to Dr. Ava Hedayatipour and Dr. Arash Sarshar for their invaluable input and for graciously serving on my thesis defense committee. Their expertise and constructive feedback have significantly contributed to the quality of this work.

To my dear friends, especially Guō Yīmò, whose mentorship, understanding, encouragement, and camaraderie has played a significant role in my ability to persevere and succeed. I feel fortunate to have such a caring and supportive circle of friends.

Lastly, I am eternally indebted to my loving parents. You have instilled in me the values of hard work and perseverance, teaching me that our determination and courage shape our destiny. Your guidance and support have been the foundation of the person I am today, and I aspire to make you proud.

This material is based upon work supported by the National Science Foundation under Grant No. \textbf{2245247}. Chapter 2 is based on the paper entitled ``Risk-Aware and Explainable Framework for Ensuring Guaranteed Coverage in Evolving Hardware Trojan Detection'' \cite{Vishwakarma:ICCAD} which has been published at the \textit{Proceedings of 42nd International Conference on Computer Aided Design (ICCAD)}. Chapter 3 is based on the paper entitled ``Uncertainty-Aware Hardware Trojan Detection Using Multimodal Deep Learning'' \cite{Vishwakarma:DATE} which has been published at the \textit{Proceedings of 27th Design, Automation \& Test in Europe Conference \& Exhibition (DATE)}.




\endgroup